FinalManuscript_DISCS_UG

### 2018-06-24 parts/01_introduction_01contextofstudy.tex

Digital data privacy and security is a growing concern in various fields, such as  cloud computing \cite{potey_homomorphic_2016}, health information systems \cite{kester_cryptographic_2015}, and video surveillance \cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys. a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite[p.119]{tilborg_encyclopedia_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over a insecure channel:  and thus much research has been done on the development and application of various cryptosystems.

One such particular application of cryptography is image encryption. While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption System (AES) or elliptic curve cryptography, can also be used to encrypt images \cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed \cite{murugan_survey_2018}.

>>>>

Digital data privacy and security is a growing concern in various fields, such as  cloud computing \cite{potey_homomorphic_2016}, health information systems \cite{kester_cryptographic_2015}, and video surveillance \cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys. a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite[p.119]{tilborg_encyclopedia_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over an insecure channel:  and thus much research has been done on the development and application of various cryptosystems.

One such particular application of cryptography is image encryption. While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption Standard (AES) or elliptic curve cryptography, can also be used to encrypt images \cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed \cite{murugan_survey_2018}.

### 2018-06-24 parts/01_introduction_02researchquestions.tex

In this study, we ask

\begin{enumerate}
    \item Research questions 1...
    \item Research questions 2...
    \item Research questions 3...
\end{enumerate}

>>>>

In this study, we ask the following main research question: What is the best method for image data to be encrypted and manipulated for practical applications?

To answer this question, we will consider the following sub-questions in our research:
\begin{enumerate}
    \item Which homomorphic image encryption algorithms are the most efficient in terms of time when applying image manipulation operations?
    \item Which homomorphic image encryption algorithms are the most secure under statistical attacks?
    \item How can a library for OpenCV be implemented for further use and study of image manipulation operations within a homomorphic cryptosystem?
\end{enumerate}

### 2018-06-24 parts/01_introduction_05scopeandlimitations.tex

\subsection{Scope of Testing}
We will implement and test the following algorithms:
\begin{enumerate}
	\item A modified version of the Paillier cryptosystem \cite{} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
	\item An elliptic curve and ElGamal based cryptosystem for homomorphic encryption presented by Li, et. al. \cite{li_elliptic_2012}.
	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry \cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Operations based on convolution
	\item Morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et. al \cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature \cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption.
	\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
		\item Noise tolerance
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis (number of pixel change rate (NPCR), universeral average change intensity (UACI))
	\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the review of related literature.

>>>>

\subsection{Scope of Testing}
We will implement and test the following algorithms:
\begin{enumerate}
	\item A modified version of the Paillier cryptosystem \cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
	\item An elliptic curve and ElGamal based cryptosystem for homomorphic encryption presented by Li, et. al. \cite{li_elliptic_2012}.
	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry \cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Operations based on convolution
	\item Morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et. al \cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature \cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption.
	\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
		\item Noise tolerance
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis (number of pixel change rate (NPCR), universeral average change intensity (UACI))
	\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the review of related literature.
